### 2020-12-11 paper/localpsf.tex
wrote weighting function algorithm at infinite dimensional level

One should only expect $\widetilde{A}(y,x)$ to be accurate for $x \in \Omega_I$, $y \in \Omega$. If $\mathcal{A}$ is symmetric then one may overwrite potentially innacurate entries $\widetilde{A}(y,x)$, $x \in \Omega_b$, $y \in \Omega_I$, with the accurate entries $\widetilde{A}(x,y)$. If $\mathcal{A}$ is nonsymmetric, one may form an accurate approximation of these entries by applying our procedure to $\mathcal{A}^T$. Our method will furnish an approximation $\widetilde{A}(y,x)$ for $x \in \Omega_B$, $y \in \Omega_B$ (the block of $\widetilde{H}$ corresponding to boundary-boundary interactions), but this part of the approximation is unlikely to satisfy Condition 1 ($\varphi_x$ varies smoothly as a function of $x$).

@@

\begin{remark}
	Computing $\mathbf{g} = K^+\mathbf{f}$ is equivalent to solving the discretized Poisson problem with $f$ as the right hand side source, with pure Neumann boundary conditions, and with the constraint that the solution has average value equal to zero. That is,
	\begin{equation*}
		\mathbf{g} = K^+ \mathbf{f} \quad \Leftrightarrow \quad 
		\begin{cases}
			\Delta g = f, & \text{in }\Omega,\\
			\nu \cdot \nabla g = 0, & \text{on }\partial \Omega,\\
			\int_\Omega g(x) dx = 0,
		\end{cases}
	\end{equation*}
	where $\nu$ denotes the normal to the boundary.

@@

The solution to this system of equations is found by the following process:
\begin{enumerate}
	\item Compute 
	\begin{equation*}
		\Psi := A^+ B^T
	\end{equation*}
	by solving Neumann poisson problems for point source right hand sides, with point sources located at the points $x_i$, $i=1,\dots,q$.
	\item Compute 
	\begin{equation*}
		\Theta := A^+ M \Psi
	\end{equation*}
	by solving Neumann Poisson problems with the columns of $\Psi$ as distributed sources.
	\item Form 
	\begin{equation*}
		S = \Psi^T M \Psi
	\end{equation*}.
	\item Compute \begin{equation*}
		\alpha = \left(\mathbf{1}^T S^{-1} \mathbf{1}\right)^{-1}\mathbf{1}^T S^{-1} \mathbf{y}.
	\end{equation*}
	\item Compute 
	\begin{equation*}
		\boldsymbol{\lambda} = -S^{-1} \left(\mathbf{y} - \alpha \mathbf{1} \right).
	\end{equation*}
	\item Compute
	\begin{equation*}
		\mathbf{u} = -\Theta \boldsymbol{\lambda} + \alpha \mathbf{c}
	\end{equation*}
\end{enumerate}

@@

\appendix
\section{Fast ellipsoid intersection test}
The procedure for choosing sample points relies on quickly determining whether two ellipsoids intersect. Let $E_p$ and $E_q$ be the ellipsoids defined as
\begin{align*}
	E_p :=& \{x : (x - \mu_p)^T \Sigma_p^{-1} (x - \mu_p) \le \tau^2\} \\
	E_q :=& \{x : (x - \mu_q)^T \Sigma_q^{-1} (x - \mu_q) \le \tau^2\}, \\
\end{align*}
where $\mu_p, \mu_q \in \mathbb{R}^d$, and $\Sigma_p, \Sigma_q \in \mathbb{R}^{d \times d}$ are positive definite. Let $K$ be the following one dimensional convex function:
\begin{equation*}
	K(s) := 1 - \frac{1}{\tau^2} (\mu_p - \mu_q)^T \left(\frac{1}{1-s}\Sigma_p + \frac{1}{s}\Sigma_q\right)^{-1}(\mu_p - \mu_q)	
\end{equation*}
In CITE it is shown that $E_p \cap E_q = \{\}$ if and only if $K(s) < 0$ for some $s\in (0,1)$. We check whether $E_p$ and $E_q$ intersect by minimizing $K(s)$ on $(0,1)$. If $K(s^*) <0$ at the minimizer $s^*$, then $E_p \cap E_q = \{\}$. Otherwise $E_p \cap E_q \neq \{\}$.

@@

\section*{Acknowledgments}
We acknowledge

>>>>

@@

\begin{remark}
	Computing $\mathbf{g} = K^+\mathbf{f}$ is equivalent to solving the discretized Poisson problem with $f$ as the right hand side source, with pure Neumann boundary conditions, and with the constraint that the solution has average value equal to zero. That is,
	\begin{equation}
	\label{eq:pure_neumann_poisson}
		\mathbf{g} = K^+ \mathbf{f} \quad \Leftrightarrow \quad 
		\begin{cases}
			\Delta g = f, & \text{in }\Omega,\\
			\nu \cdot \nabla g = 0, & \text{on }\partial \Omega,\\
			\int_\Omega g(x) dx = 0,
		\end{cases}
	\end{equation}
	where $\nu$ denotes the normal to the boundary.

@@

	%	\Output{Spatially varying mean $\mu:\Omega \rightarrow \mathbb{R}^d$, \\ 
	%		Spatially varying covariance $\Sigma:\Omega \rightarrow \mathbb{R}^{d \times d}$}
	%	\Begin{
	{	
		\For{$i=1,2, \dots, r$}{
			Compute $\psi_i$ as the solution to following Poisson problem with pure Neumann boundary conditions and a point source at $x_i$:
			$$\begin{cases}
			\Delta \psi_i = \delta_{x_i}, & \text{in }\Omega,\\
			\nu \cdot \nabla \psi_i = 0, & \text{on }\partial \Omega,\\
			\int_\Omega \psi_i(x) dx = 0.
			\end{cases}$$

			Compute $\theta_i$ as the solution to the following Poisson problem with pure Neumann boundary conditions and source $\psi_i$:
			$$\begin{cases}
			\Delta \theta_i = \psi_i, & \text{in }\Omega,\\
			\nu \cdot \nabla \theta_i = 0, & \text{on }\partial \Omega,\\
			\int_\Omega \theta_i(x) dx = 0.
			\end{cases}$$
		}

		Form the $r \times r$ matrix $S$ with entries
		$$S_{ij} = \left(\psi_i, \psi_j\right)_{L^2(\Omega)}.$$

		\For{$i=1,2,\dots,r$}{
			Compute
			$$\alpha = \frac{\mathbf{1}^T S^{-1} e_i}{\mathbf{1}^T S^{-1} \mathbf{1}},$$
			where $\mathbf{1} = (1,1,\dots,1)$ is the length $r$ vector which has all components equal to one, and $e_i = (0,\dots,0,1,0,\dots,0)$ is the length $r$ vector with $i^\text{th}$ component equal to one and all other components equal to zero.

			Compute 
			\begin{equation*}
			\lambda = -S^{-1} \left(e_i - \alpha \mathbf{1} \right).
			\end{equation*}

			Compute
			$$w_i = -\sum_{k=1}^r \lambda_k \theta_k + \alpha C,$$
			where we recall that $C$ is the constant function $C(x)=1$ on $\Omega$.
		}
	}
	\caption{Compute weighting functions $w_i$, $i=1,\dots,r$.}
	\label{alg:weighting_functions_incremental}
\end{algorithm2e}

The solution to this system of equations is found by the following process:
\begin{enumerate}
	\item Compute 
	\begin{equation*}
		\Psi := K^+ E^T
	\end{equation*}
	by solving Neumann poisson problems for point source right hand sides, with point sources located at the points $x_i$, $i=1,\dots,q$.
	\item Compute 
	\begin{equation*}
		\Theta := K^+ M \Psi
	\end{equation*}
	by solving Neumann Poisson problems with the columns of $\Psi$ as distributed sources.
	\item Form 
	\begin{equation*}
		S = \Psi^T M \Psi
	\end{equation*}.
	\item Compute \begin{equation*}
		\alpha = \left(\mathbf{1}^T S^{-1} \mathbf{1}\right)^{-1}\mathbf{1}^T S^{-1} \mathbf{y}.
	\end{equation*}
	\item Compute 
	\begin{equation*}
		\boldsymbol{\lambda} = -S^{-1} \left(\mathbf{y} - \alpha \mathbf{1} \right).
	\end{equation*}
	\item Compute
	\begin{equation*}
		\mathbf{u} = -\Theta \boldsymbol{\lambda} + \alpha \mathbf{c}
	\end{equation*}
\end{enumerate}

@@

\appendix

\section{Discretized algorithms}

\section{Fast ellipsoid intersection test}
The procedure for choosing sample points relies on quickly determining whether two ellipsoids intersect. Let $E_p$ and $E_q$ be the ellipsoids defined as
\begin{align*}
	E_p :=& \{x : (x - \mu_p)^T \Sigma_p^{-1} (x - \mu_p) \le \tau^2\} \\
	E_q :=& \{x : (x - \mu_q)^T \Sigma_q^{-1} (x - \mu_q) \le \tau^2\}, \\
\end{align*}
where $\mu_p, \mu_q \in \mathbb{R}^d$, and $\Sigma_p, \Sigma_q \in \mathbb{R}^{d \times d}$ are positive definite. Let $K$ be the following one dimensional convex function:
\begin{equation*}
	K(s) := 1 - \frac{1}{\tau^2} (\mu_p - \mu_q)^T \left(\frac{1}{1-s}\Sigma_p + \frac{1}{s}\Sigma_q\right)^{-1}(\mu_p - \mu_q)	
\end{equation*}
In CITE it is shown that $E_p \cap E_q = \{\}$ if and only if $K(s) < 0$ for some $s\in (0,1)$. We check whether $E_p$ and $E_q$ intersect by minimizing $K(s)$ on $(0,1)$. If $K(s^*) <0$ at the minimizer $s^*$, then $E_p \cap E_q = \{\}$. Otherwise $E_p \cap E_q \neq \{\}$.

@@

One should only expect $\widetilde{A}(y,x)$ to be accurate for $x \in \Omega_I$, $y \in \Omega$. If $\mathcal{A}$ is symmetric then one may overwrite potentially inaccurate entries $\widetilde{A}(y,x)$, $x \in \Omega_b$, $y \in \Omega_I$, with the accurate entries $\widetilde{A}(x,y)$. If $\mathcal{A}$ is nonsymmetric, one may form an accurate approximation of these entries by applying our procedure to $\mathcal{A}^T$. Our method will furnish an approximation $\widetilde{A}(y,x)$ for $x \in \Omega_B$, $y \in \Omega_B$ (the block of $\widetilde{H}$ corresponding to boundary-boundary interactions), but this part of the approximation is unlikely to satisfy Condition 1 ($\varphi_x$ varies smoothly as a function of $x$).

\section*{Acknowledgments}
We thank J.J. Alger for helpful discussions
